---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(chad)
library(sf)
```

# chad: Datasets for Use in Designing Surveys in Chad

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/spatialworks/chad/workflows/R-CMD-check/badge.svg)](https://github.com/spatialworks/chad/actions)
[![CodeFactor](https://www.codefactor.io/repository/github/spatialworks/chad/badge)](https://www.codefactor.io/repository/github/spatialworks/chad)
<!-- badges: end -->

Designing surveys require relevant datasets to be used as basis for sample size calculations, sampling design, survey planning/logistics and survey implementation. These include datasets on population, lists of sampling clusters, map datasets for spatial sampling, and previous survey datasets that can be used for estimating indicator variance and design effects. This package contains relevant datasets for use in designing surveys in Chad.

## Installation

The development version of the `{chad}` package can be installed from [GitHub](https://github.com/) with:

``` r
if (!require(remotes)) install.packages("remotes")
remotes::install_github("spatialworks/chad")
```

## Usage

### Region borders

The Chad region borders is accessed via the `regions` dataset.

```{r}
chad::regions
```

The regions borders of Chad can be plotted by:

```{r}
plot(chad::regions, max.plot = 1, col = NA, main = NULL)
```
